Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-06-10 report/report.tex
Fix duplicate citations

% TODO: Mention that positional accuracy will be focused on, and the implications of not fixing errors when converting to a 3D model
When it comes to the quality of available data, it turns out that in practise, geodata databases without errors are rare.
Among the most common errors are missing or invalid geometry, and invalid semantics.
However, \textbf{(Biljecki, Ledoux and Stoter, 2016, 1)} note that there are coming more and more sophisticated methods for automatically correcting the most common errors.
Geodata validation and correction is only an emerging field of research.
and many such datasets were usually obtained years ago, and creating error-free datasets was neither possible due to the lack of validation techniques, nor a high priority.

@@

Another crucial concept in city modelling is the Level Of Detail (LOD) aspect.
\textbf{(Biljecki, Ledoux and Stoter, 2016, 1)} provide an extensive overview of the concept of LOD in GIS mapping.
They provide the GityGML definition of LOD as a series of different 3D representation of the same data, at different detail levels, and the LOD chosen for a particulary application suggests how the data has been aqquired and modelled.
The CityGML standard divides the LOD representation of 3D models into three classes: A B and C.
\begin{enumerate}
    \item LOD-A models are renderings of the building footprint itself, or rectangular building blocks that have been extruded from the footprint to give the building height.
    \item LOD-B models are building blocks with simplifed roof shapes.
    \item LOD-C models are LOD-B models which include features such as doors, windows, alcoves, building decor, indoor features or vegetation.
\end{enumerate}
A modeler may chose what LOD class(es) to use depending on data availablity and application.

%TODO: Summarize both sources by Biljecki
\textbf{Biljecki, Ledoux and Stoter, 2016, 1}
\textbf{Biljecki et al, 2016, 2}

@@

Yet another challenge lies in producing highly detailed 3D models of buildings at a consistent rate.
Recall the concept of Level of Detail, as presented by \textbf{(Biljecki, Ledoux and Stoter, 2016, 1)} in section *** of this report.
It turns out that, with the current means of data aquisition from OSM being limited to building footprints, using OSM data a model can only produce LOB-B models at best.
If a modeler wishes to aqquire building assets at a LOD-C level, they would have to complete the data with other sources, or rely on procedural methods to populate crude city models with additional details and building features that give the models more aestethic depth, but do not neccessarily reflect reality.

@@

\bibitem{biljecki-16-1}
Biljecki, F., Ledoux, H., Stoter, J. (2016, 1): An improved LOD specification for 3D building models. Computers, Environment, and Urban Systems, vol. 59, 25-37.

\bibitem{biljecki-16-2}
Biljecki, F., Ledoux, H., Du, X., Stoter, J., Soon, K., and Khoo, V. (2016, 2). The most common geometric and semantic errors in CityGML datasets. 10.5194/isprs-annals-IV-2-W1-13-2016. 
\bibitem{biljecki-17}
Biljecki, F., Ledoux, H. and Stoter, J. (2017). Generating 3D city models without elevation data. Computers Environment and Urban Systems. 64. 1-18. 10.1016/j.compenvurbsys.2017.01.001. 
\bibitem{douglas-73}
Douglas, D.H. and Peucker T.K. (1973). Algorithms for the Reduction of the Number of Points Required to Represent a Digitalized Line or Its Caricature. Cartographica: The International Journal for Geographic Information and Geovisualization, 10(2), 112-122.

>>>>

% TODO: Mention that positional accuracy will be focused on, and the implications of not fixing errors when converting to a 3D model
When it comes to the quality of available data, it turns out that in practise, geodata databases without errors are rare.
Among the most common errors are missing or invalid geometry, and invalid semantics.
However, \textbf{(Biljecki, Ledoux and Stoter, 2016 (1))} note that there are coming more and more sophisticated methods for automatically correcting the most common errors.
Geodata validation and correction is only an emerging field of research.
and many such datasets were usually obtained years ago, and creating error-free datasets was neither possible due to the lack of validation techniques, nor a high priority.

@@

Another crucial concept in city modelling is the Level Of Detail (LOD) aspect.
\textbf{(Biljecki, Ledoux and Stoter, 2016 (1))} provide an extensive overview of the concept of LOD in GIS mapping.
They provide the GityGML definition of LOD as a series of different 3D representation of the same data, at different detail levels, and the LOD chosen for a particulary application suggests how the data has been aqquired and modelled.
The CityGML standard divides the LOD representation of 3D models into three classes: A B and C.
\begin{enumerate}
    \item LOD-A models are renderings of the building footprint itself, or rectangular building blocks that have been extruded from the footprint to give the building height.
    \item LOD-B models are building blocks with simplifed roof shapes.
    \item LOD-C models are LOD-B models which include features such as doors, windows, alcoves, building decor, indoor features or vegetation.
\end{enumerate}
A modeler may chose what LOD class(es) to use depending on data availablity and application.

%TODO: Summarize both sources by Biljecki
\textbf{Biljecki, Ledoux and Stoter, 2016 (1)}
\textbf{Biljecki et al, 2016, 2}

@@

Yet another challenge lies in producing highly detailed 3D models of buildings at a consistent rate.
Recall the concept of Level of Detail, as presented by \textbf{(Biljecki, Ledoux and Stoter, 2016 (1))} in section *** of this report.
It turns out that, with the current means of data aquisition from OSM being limited to building footprints, using OSM data a model can only produce LOB-B models at best.
If a modeler wishes to aqquire building assets at a LOD-C level, they would have to complete the data with other sources, or rely on procedural methods to populate crude city models with additional details and building features that give the models more aestethic depth, but do not neccessarily reflect reality.

@@

\bibitem{biljecki-16-1}
Biljecki, F., Ledoux, H., Stoter, J. (2016 (1)): An improved LOD specification for 3D building models. Computers, Environment, and Urban Systems, vol. 59, 25-37.

\bibitem{biljecki-16-2}
    Biljecki, F., Ledoux, H., Du, X., Stoter, J., Soon, K., and Khoo, V. (2016 (2)). The most common geometric and semantic errors in CityGML datasets. 10.5194/isprs-annals-IV-2-W1-13-2016. 
\bibitem{biljecki-17}
Biljecki, F., Ledoux, H. and Stoter, J. (2017). Generating 3D city models without elevation data. Computers Environment and Urban Systems. 64. 1-18. 10.1016/j.compenvurbsys.2017.01.001. 
\bibitem{douglas-73}
Douglas, D.H. and Peucker T.K. (1973). Algorithms for the Reduction of the Number of Points Required to Represent a Digitalized Line or Its Caricature. Cartographica: The International Journal for Geographic Information and Geovisualization, 10(2), 112-122.
